A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-12 Simulator/article.tex
la2pdf commit - 2014:05:13	00:29:57	(Tue13.May)
la2pdf commit - 2014:05:13	01:05:48	(Tue13.May)

Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$.

\begin{align}
\P = \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\end{align}
where
\begin{align*}
l &= x_\text{min}  &  r &= x_\text{max}\\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

>>>>

Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$. There are two main types of projection, perspective and orthographic. Perspective projection scales all $x$ and $y$ coordinates inversely with the distance to the objects to create a sense of perspective in the image. Orthographic projection, on the other hand, maps all the scene's vertices to a squared cube where each dimension has the range [-1,1]. This will render all objects equally large whether they are in the distance or up close. Its projection matrix is defined as
\begin{align}
\P = \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\end{align}
where $l,r,b,t,n$ and $f$ are left, right, bottom, top, near and far boundaries of the projection plane, respectively.
\begin{align*}
l &= x_\text{min}  &  r &= x_\text{max}\\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/opengl_part.svg}%
\caption{Setting camera top and bottom boundaries.}\label{camera_top_bottom}%
\end{figure}
